
\documentclass[11pt, letterpaper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}
\pagestyle{empty}
\begin{document}
\setlength{\parindent}{0.5em}
\setlength{\parskip}{1.4em}

\newpage \section*{\LARGE Football Picks 2017: Week 1}
\noindent \normalsize \textbf{Thursday, SEP. 7} \par
Kansas City Chiefs @ New England Patriots (5:30pm)\par
\noindent \normalsize \textbf{Sunday, SEP. 10} \par
New York Jets @ Buffalo Bills (10:00am)\par
Atlanta Falcons @ Chicago Bears (10:00am)\par
Baltimore Ravens @ Cincinnati Bengals (10:00am)\par
Pittsburgh Steelers @ Cleveland Browns (10:00am)\par
Arizona Cardinals @ Detroit Lions (10:00am)\par
Jacksonville Jaguars @ Houston Texans (10:00am)\par
Tampa Bay Buccaneers @ Miami Dolphins (10:00am)\par
Oakland Raiders @ Tennessee Titans (10:00am)\par
Philadelphia Eagles @ Washington Redskins (10:00am)\par
Indianapolis Colts @ Los Angeles Rams (1:05pm)\par
Seattle Seahawks @ Green Bay Packers (1:25pm)\par
Carolina Panthers @ San Francisco 49ers (1:25pm)\par
New York Giants @ Dallas Cowboys (5:30pm)\par
\noindent \normalsize \textbf{Monday, SEP. 11} \par
New Orleans Saints @ Minnesota Vikings (4:10pm)\par
Los Angeles Chargers @ Denver Broncos (7:20pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 2}
\noindent \normalsize \textbf{Thursday, SEP.    14} \par
Houston Texans @ Cincinnati Bengals (5:25pm)\par
\noindent \normalsize \textbf{Sunday, SEP. 17} \par
Cleveland Browns @ Baltimore Ravens (10:00am)\par
Buffalo Bills @ Carolina Panthers (10:00am)\par
Arizona Cardinals @ Indianapolis Colts (10:00am)\par
Tennessee Titans @ Jacksonville Jaguars (10:00am)\par
Philadelphia Eagles @ Kansas City Chiefs (10:00am)\par
New England Patriots @ New Orleans Saints (10:00am)\par
Minnesota Vikings @ Pittsburgh Steelers (10:00am)\par
Chicago Bears @ Tampa Bay Buccaneers (10:00am)\par
Miami Dolphins @ Los Angeles Chargers (1:05pm)\par
New York Jets @ Oakland Raiders (1:05pm)\par
Dallas Cowboys @ Denver Broncos (1:25pm)\par
Washington Redskins @ Los Angeles Rams (1:25pm)\par
San Francisco 49ers @ Seattle Seahawks (1:25pm)\par
Green Bay Packers @ Atlanta Falcons (5:30pm)\par
\noindent \normalsize \textbf{Monday, SEP. 18} \par
Detroit Lions @ New York Giants (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 3}
\noindent \normalsize \textbf{Thursday, SEP.    21} \par
Los Angeles Rams @ San Francisco 49ers (5:25pm)\par
\noindent \normalsize \textbf{Sunday, SEP. 24} \par
Baltimore Ravens @ Jacksonville Jaguars    (L) (6:30a)\par
Denver Broncos @ Buffalo Bills (10:00am)\par
New Orleans Saints @ Carolina Panthers (10:00am)\par
Pittsburgh Steelers @ Chicago Bears (10:00am)\par
Atlanta Falcons @ Detroit Lions (10:00am)\par
Cleveland Browns @ Indianapolis Colts (10:00am)\par
Tampa Bay Buccaneers @ Minnesota Vikings (10:00am)\par
Houston Texans @ New England Patriots (10:00am)\par
Miami Dolphins @ New York Jets (10:00am)\par
New York Giants @ Philadelphia Eagles (10:00am)\par
Seattle Seahawks @ Tennessee Titans (1:05pm)\par
Cincinnati Bengals @ Green Bay Packers (1:25pm)\par
Kansas City Chiefs @ Los Angeles Chargers (1:25pm)\par
Oakland Raiders @ Washington Redskins (5:30pm)\par
\noindent \normalsize \textbf{Monday, SEP. 25} \par
Dallas Cowboys @ Arizona Cardinals (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 4}
\noindent \normalsize \textbf{Thursday, SEP.    28} \par
Chicago Bears @ Green Bay Packers (5:25pm)\par
\noindent \normalsize \textbf{Sunday, OCT. 1} \par
New Orleans Saints @ Miami Dolphins (L) (6:30a)\par
Buffalo Bills @ Atlanta Falcons (10:00am)\par
Pittsburgh Steelers @ Baltimore Ravens (10:00am)\par
Cincinnati Bengals @ Cleveland Browns (10:00am)\par
Los Angeles Rams @ Dallas Cowboys (10:00am)\par
Tennessee Titans @ Houston Texans (10:00am)\par
Detroit Lions @ Minnesota Vikings (10:00am)\par
Carolina Panthers @ New England Patriots (10:00am)\par
Jacksonville Jaguars @ New York Jets (10:00am)\par
San Francisco 49ers @ Arizona Cardinals (1:05pm)\par
Philadelphia Eagles @ Los Angeles Chargers (1:05pm)\par
New York Giants @ Tampa Bay Buccaneers (1:05pm)\par
Oakland Raiders @ Denver Broncos (1:25pm)\par
Indianapolis Colts @ Seattle Seahawks (5:30pm)\par
\noindent \normalsize \textbf{Monday, OCT. 2} \par
Washington Redskins @ Kansas City Chiefs (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 5}
\noindent \normalsize \textbf{Thursday, OCT. 5} \par
New England Patriots @ Tampa Bay Buccaneers (5:25pm)\par
\noindent \normalsize \textbf{Sunday, OCT. 8} \par
Buffalo Bills @ Cincinnati Bengals (10:00am)\par
New York Jets @ Cleveland Browns (10:00am)\par
Carolina Panthers @ Detroit Lions (10:00am)\par
San Francisco 49ers @ Indianapolis Colts (10:00am)\par
Tennessee Titans @ Miami Dolphins (10:00am)\par
Los Angeles Chargers @ New York Giants (10:00am)\par
Arizona Cardinals @ Philadelphia Eagles (10:00am)\par
Jacksonville Jaguars @ Pittsburgh Steelers (10:00am)\par
Seattle Seahawks @ Los Angeles Rams (1:05pm)\par
Baltimore Ravens @ Oakland Raiders (1:05pm)\par
Green Bay Packers @ Dallas Cowboys (1:25pm)\par
Kansas City Chiefs @ Houston Texans * (5:30pm)\par
\noindent \normalsize \textbf{Monday, OCT. 9} \par
Minnesota Vikings @ Chicago Bears (5:30pm)\par
\vfill{}
Byes:  Atlanta,  Denver,  New Orleans, 
                      Washington
\newpage \section*{\LARGE Football Picks 2017: Week 6}
\noindent \normalsize \textbf{Thursday, OCT.    12} \par
Philadelphia Eagles @ Carolina Panthers (5:25pm)\par
\noindent \normalsize \textbf{Sunday, OCT. 15} \par
Miami Dolphins @ Atlanta Falcons (10:00am)\par
Chicago Bears @ Baltimore Ravens (10:00am)\par
Cleveland Browns @ Houston Texans (10:00am)\par
Green Bay Packers @ Minnesota Vikings (10:00am)\par
Detroit Lions @ New Orleans Saints (10:00am)\par
New England Patriots @ New York Jets (10:00am)\par
San Francisco 49ers @ Washington Redskins (10:00am)\par
Tampa Bay Buccaneers @ Arizona Cardinals (1:05pm)\par
Los Angeles Rams @ Jacksonville Jaguars (1:05pm)\par
Pittsburgh Steelers @ Kansas City Chiefs (1:25pm)\par
Los Angeles Chargers @ Oakland Raiders (1:25pm)\par
New York Giants @ Denver Broncos * (5:30pm)\par
\noindent \normalsize \textbf{Monday, OCT. 16} \par
Indianapolis Colts @ Tennessee Titans (5:30pm)\par
\vfill{}
Byes:  Buffalo,  Cincinnati,  Dallas, 
                      Seattle
\newpage \section*{\LARGE Football Picks 2017: Week 7}
\noindent \normalsize \textbf{Thursday, OCT.    19, 2017} \par
Kansas City Chiefs @ Oakland Raiders (5:25pm)\par
\noindent \normalsize \textbf{Sunday, OCT. 22, 2017} \par
Tampa Bay Buccaneers @ Buffalo Bills (10:00am)\par
Carolina Panthers @ Chicago Bears (10:00am)\par
Tennessee Titans @ Cleveland Browns (10:00am)\par
New Orleans Saints @ Green Bay Packers (10:00am)\par
Jacksonville Jaguars @ Indianapolis Colts (10:00am)\par
Arizona Cardinals @ Los Angeles Rams (L) (10:00am)\par
New York Jets @ Miami Dolphins (10:00am)\par
Baltimore Ravens @ Minnesota Vikings (10:00am)\par
Cincinnati Bengals @ Pittsburgh Steelers (10:00am)\par
Dallas Cowboys @ San Francisco 49ers (1:05pm)\par
Denver Broncos @ Los Angeles Chargers (1:25pm)\par
Seattle Seahawks @ New York Giants (1:25pm)\par
Atlanta Falcons @ New England Patriots * (5:30pm)\par
\noindent \normalsize \textbf{Monday, OCT. 23, 2017} \par
Washington Redskins @ Philadelphia Eagles (5:30pm)\par
\vfill{}
Byes:  Detroit,  Houston
\newpage \section*{\LARGE Football Picks 2017: Week 8}
\noindent \normalsize \textbf{Thursday, OCT.    26, 2017} \par
Miami Dolphins @ Baltimore Ravens (5:25pm)\par
\noindent \normalsize \textbf{Sunday, OCT. 29, 2017} \par
Minnesota Vikings @ Cleveland Browns (L) (6:30a)\par
Oakland Raiders @ Buffalo Bills (10:00am)\par
Indianapolis Colts @ Cincinnati Bengals (10:00am)\par
Los Angeles Chargers @ New England Patriots (10:00am)\par
Chicago Bears @ New Orleans Saints (10:00am)\par
Atlanta Falcons @ New York Jets (10:00am)\par
San Francisco 49ers @ Philadelphia Eagles (10:00am)\par
Carolina Panthers @ Tampa Bay Buccaneers (10:00am)\par
Houston Texans @ Seattle Seahawks (1:05pm)\par
Dallas Cowboys @ Washington Redskins (1:25pm)\par
Pittsburgh Steelers @ Detroit Lions * (5:30pm)\par
\noindent \normalsize \textbf{Monday, OCT. 30, 2017} \par
Denver Broncos @ Kansas City Chiefs (5:30pm)\par
\vfill{}
Byes:  Arizona,  Green Bay,     Jacksonville, 
                      Los Angeles Rams,   Giants,  Tennessee
\newpage \section*{\LARGE Football Picks 2017: Week 9}
\noindent \normalsize \textbf{Thursday, NOV.    2, 2017} \par
Buffalo Bills @ New York Jets (5:25pm)\par
\noindent \normalsize \textbf{Sunday, NOV. 5, 2017} \par
Atlanta Falcons @ Carolina Panthers (10:00am)\par
Indianapolis Colts @ Houston Texans (10:00am)\par
Cincinnati Bengals @ Jacksonville Jaguars (10:00am)\par
Tampa Bay Buccaneers @ New Orleans Saints (10:00am)\par
Los Angeles Rams @ New York Giants (10:00am)\par
Denver Broncos @ Philadelphia Eagles (10:00am)\par
Baltimore Ravens @ Tennessee Titans (10:00am)\par
Arizona Cardinals @ San Francisco 49ers (1:05pm)\par
Washington Redskins @ Seattle Seahawks (1:05pm)\par
Kansas City Chiefs @ Dallas Cowboys (1:25pm)\par
Oakland Raiders @ Miami Dolphins * (5:30pm)\par
\noindent \normalsize \textbf{Monday, NOV. 6, 2017} \par
Detroit Lions @ Green Bay Packers (5:30pm)\par
\vfill{}
Byes: Chicago,  Cleveland,  Los    Angeles
                      Chargers,  Minnesota,  New England,  Pittsburgh
\newpage \section*{\LARGE Football Picks 2017: Week 10}
\noindent \normalsize \textbf{Thursday, NOV.    9, 2017} \par
Seattle Seahawks @ Arizona Cardinals (5:25pm)\par
\noindent \normalsize \textbf{Sunday, NOV. 12, 2017} \par
New Orleans Saints @ Buffalo Bills (10:00am)\par
Green Bay Packers @ Chicago Bears (10:00am)\par
Cleveland Browns @ Detroit Lions (10:00am)\par
Pittsburgh Steelers @ Indianapolis Colts (10:00am)\par
Los Angeles Chargers @ Jacksonville Jaguars (10:00am)\par
New York Jets @ Tampa Bay Buccaneers (10:00am)\par
Cincinnati Bengals @ Tennessee Titans (10:00am)\par
Minnesota Vikings @ Washington Redskins (10:00am)\par
Houston Texans @ Los Angeles Rams (1:05pm)\par
Dallas Cowboys @ Atlanta Falcons (1:25pm)\par
New York Giants @ San Francisco 49ers (1:25pm)\par
New England Patriots @ Denver Broncos * (5:30pm)\par
\noindent \normalsize \textbf{Monday, NOV. 13, 2017} \par
Miami Dolphins @ Carolina Panthers (5:30pm)\par
\vfill{}
Byes:  Baltimore,  Kansas City,     Oakland, 
                      Philadelphia
\newpage \section*{\LARGE Football Picks 2017: Week 11}
\noindent \normalsize \textbf{Thursday, NOV.    16, 2017} \par
Tennessee Titans @ Pittsburgh Steelers (5:25pm)\par
\noindent \normalsize \textbf{Sunday, NOV. 19, 2017} \par
Detroit Lions @ Chicago Bears (10:00am)\par
Jacksonville Jaguars @ Cleveland Browns (10:00am)\par
Baltimore Ravens @ Green Bay Packers (10:00am)\par
Arizona Cardinals @ Houston Texans (10:00am)\par
Los Angeles Rams @ Minnesota Vikings (10:00am)\par
Washington Redskins @ New Orleans Saints (10:00am)\par
Kansas City Chiefs @ New York Giants (10:00am)\par
Buffalo Bills @ Los Angeles Chargers (1:05pm)\par
Cincinnati Bengals @ Denver Broncos (1:25pm)\par
New England Patriots @ Oakland Raiders    (MC) (1:25pm)\par
Philadelphia Eagles @ Dallas Cowboys * (5:30pm)\par
\noindent \normalsize \textbf{Monday, NOV. 20, 2017} \par
Atlanta Falcons @ Seattle Seahawks (5:30pm)\par
\vfill{}
Byes:  Carolina,  Indianapolis,     Miami, 
                      New York Jets,  San Francisco,  Tampa Bay
\newpage \section*{\LARGE Football Picks 2017: Week 12}
\noindent \normalsize \textbf{Thursday, NOV.    23, 2017} \par
Minnesota Vikings @ Detroit Lions (9:30pm)\par
Los Angeles Chargers @ Dallas Cowboys (1:30pm)\par
New York Giants @ Washington Redskins (5:30pm)\par
\noindent \normalsize \textbf{Sunday, NOV. 26, 2017} \par
Tampa Bay Buccaneers @ Atlanta Falcons (10:00am)\par
Cleveland Browns @ Cincinnati Bengals (10:00am)\par
Tennessee Titans @ Indianapolis Colts (10:00am)\par
Buffalo Bills @ Kansas City Chiefs (10:00am)\par
Miami Dolphins @ New England Patriots (10:00am)\par
Carolina Panthers @ New York Jets (10:00am)\par
Chicago Bears @ Philadelphia Eagles (10:00am)\par
New Orleans Saints @ Los Angeles Rams (1:05pm)\par
Seattle Seahawks @ San Francisco 49ers (1:05pm)\par
Jacksonville Jaguars @ Arizona Cardinals (1:25pm)\par
Denver Broncos @ Oakland Raiders (1:25pm)\par
Green Bay Packers @ Pittsburgh Steelers * (5:30pm)\par
\noindent \normalsize \textbf{Monday, NOV. 27, 2017} \par
Houston Texans @ Baltimore Ravens (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 13}
\noindent \normalsize \textbf{Thursday, NOV.    30, 2017} \par
Washington Redskins @ Dallas Cowboys (5:25pm)\par
\noindent \normalsize \textbf{Sunday, DEC. 3, 2017} \par
Minnesota Vikings @ Atlanta Falcons (10:00am)\par
Detroit Lions @ Baltimore Ravens (10:00am)\par
New England Patriots @ Buffalo Bills (10:00am)\par
San Francisco 49ers @ Chicago Bears (10:00am)\par
Tampa Bay Buccaneers @ Green Bay Packers (10:00am)\par
Indianapolis Colts @ Jacksonville Jaguars (10:00am)\par
Denver Broncos @ Miami Dolphins (10:00am)\par
Carolina Panthers @ New Orleans Saints (10:00am)\par
Kansas City Chiefs @ New York Jets (10:00am)\par
Houston Texans @ Tennessee Titans (10:00am)\par
Cleveland Browns @ Los Angeles Chargers (1:05pm)\par
Los Angeles Rams @ Arizona Cardinals (1:25pm)\par
New York Giants @ Oakland Raiders (1:25pm)\par
Philadelphia Eagles @ Seattle Seahawks * (5:30pm)\par
\noindent \normalsize \textbf{Monday, DEC. 4, 2017} \par
Pittsburgh Steelers @ Cincinnati Bengals (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 14}
New Orleans    Saints @ Atlanta Falcons (5:25pm)\par
\noindent \normalsize \textbf{Sunday, DEC. 10, 2017} \par
Indianapolis Colts @ Buffalo Bills (10:00am)\par
Minnesota Vikings @ Carolina Panthers (10:00am)\par
Chicago Bears @ Cincinnati Bengals (10:00am)\par
Green Bay Packers @ Cleveland Browns (10:00am)\par
San Francisco 49ers @ Houston Texans (10:00am)\par
Seattle Seahawks @ Jacksonville Jaguars (10:00am)\par
Oakland Raiders @ Kansas City Chiefs (10:00am)\par
Detroit Lions @ Tampa Bay Buccaneers (10:00am)\par
Tennessee Titans @ Arizona Cardinals (1:05pm)\par
New York Jets @ Denver Broncos (1:05pm)\par
Washington Redskins @ Los Angeles Chargers (1:05pm)\par
Philadelphia Eagles @ Los Angeles Rams (1:25pm)\par
Dallas Cowboys @ New York Giants (1:25pm)\par
Baltimore Ravens @ Pittsburgh Steelers * (5:30pm)\par
\noindent \normalsize \textbf{Monday, DEC. 11, 2017} \par
New England Patriots @ Miami Dolphins (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 15}
\noindent \normalsize \textbf{Thursday, DEC.    14, 2017} \par
Denver Broncos @ Indianapolis Colts (5:25pm)\par
\noindent \normalsize \textbf{Saturday, DEC. 16, 2017} \par
Chicago Bears @ Detroit Lions (1:30pm)\par
Los Angeles Chargers @ Kansas City Chiefs (5:25pm)\par
\noindent \normalsize \textbf{Sunday, DEC. 17, 2017} \par
Miami Dolphins @ Buffalo Bills (10:00am)\par
Green Bay Packers @ Carolina Panthers (10:00am)\par
Baltimore Ravens @ Cleveland Browns (10:00am)\par
Houston Texans @ Jacksonville Jaguars (10:00am)\par
Cincinnati Bengals @ Minnesota Vikings (10:00am)\par
New York Jets @ New Orleans Saints (10:00am)\par
Philadelphia Eagles @ New York Giants (10:00am)\par
Arizona Cardinals @ Washington Redskins (10:00am)\par
Los Angeles Rams @ Seattle Seahawks (1:05pm)\par
New England Patriots @ Pittsburgh Steelers (1:25pm)\par
Tennessee Titans @ San Francisco 49ers (1:25pm)\par
Dallas Cowboys @ Oakland Raiders * (5:30pm)\par
\noindent \normalsize \textbf{Monday, DEC. 18, 2017} \par
Atlanta Falcons @ Tampa Bay Buccaneers (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 16}
\noindent \normalsize \textbf{Saturday, DEC.    23, 2017} \par
Indianapolis Colts @ Baltimore Ravens (1:30pm)\par
Minnesota Vikings @ Green Bay Packers (5:30pm)\par
\noindent \normalsize \textbf{Sunday, DEC. 24, 2017} \par
Tampa Bay Buccaneers @ Carolina Panthers (10:00am)\par
Cleveland Browns @ Chicago Bears (10:00am)\par
Detroit Lions @ Cincinnati Bengals (10:00am)\par
Miami Dolphins @ Kansas City Chiefs (10:00am)\par
Buffalo Bills @ New England Patriots (10:00am)\par
Atlanta Falcons @ New Orleans Saints (10:00am)\par
Los Angeles Chargers @ New York Jets (10:00am)\par
Los Angeles Rams @ Tennessee Titans (10:00am)\par
Denver Broncos @ Washington Redskins (10:00am)\par
Jacksonville Jaguars @ San Francisco 49ers (1:05pm)\par
New York Giants @ Arizona Cardinals (1:25pm)\par
Seattle Seahawks @ Dallas Cowboys (1:25pm)\par
\noindent \normalsize \textbf{Monday, DEC. 25, 2017} \par
Pittsburgh Steelers @ Houston Texans (1:30pm)\par
Oakland Raiders @ Philadelphia Eagles (5:30pm)\par
\newpage \section*{\LARGE Football Picks 2017: Week 17}
\noindent \normalsize \textbf{Sunday, JAN. 1} \par
Carolina    Panthers @ Atlanta Falcons (10:00am)\par
Cincinnati Bengals @ Baltimore Ravens (10:00am)\par
Green Bay Packers @ Detroit Lions (10:00am)\par
Houston Texans @ Indianapolis Colts (10:00am)\par
Buffalo Bills @ Miami Dolphins (10:00am)\par
Chicago Bears @ Minnesota Vikings (10:00am)\par
New York Jets @ New England Patriots (10:00am)\par
Washington Redskins @ New York Giants (10:00am)\par
Dallas Cowboys @ Philadelphia Eagles (10:00am)\par
Cleveland Browns @ Pittsburgh Steelers (10:00am)\par
New Orleans Saints @ Tampa Bay Buccaneers (10:00am)\par
Jacksonville Jaguars @ Tennessee Titans (10:00am)\par
Kansas City Chiefs @ Denver Broncos (1:25pm)\par
Oakland Raiders @ Los Angeles Chargers (1:25pm)\par
San Francisco 49ers @ Los Angeles Rams (1:25pm)\par
Arizona Cardinals @ Seattle Seahawks (1:25pm)\par\end{document}